\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the nim paper

The second method is to compare the experimental ADCs to the energy deposited in 
GEANT4 by similar simulated tracks (using the same elastic events than for the drift 
paths calibration). This requires a very good GEANT4 simulation 
including drift paths, but also the spread of the charges along the path
before reaching the pad, so that the simulated hits match the experimental 
ones. Moreover, the simulation has to match the data acquisition (DAQ) features 
that can lead to cutting out hits. After setting the simulation properly, we 
compared simulation to experiment on an event by event basis as in 
figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
as the ratio of the measured ADCs to the simulated deposited energy.
Then, the ADC value of each pad is compared to 
the ADCs of the other pads inside each track.
{\bf \color{red} Mohammad: Detail are missing here.}
Results of this second method are shown in Figure~\ref{fig:dedx_p_exp_2nd},
from these we concluded that the gains of the 
second method match best the theoretical lines.

>>>>

The second method is to compare the experimental ADCs to the energy deposited in 
GEANT4 by similar simulated tracks (using the same elastic events than for the drift 
paths calibration). This requires a very good GEANT4 simulation 
including drift paths, but also the spread of the charges along the path
before reaching the pad, so that the simulated hits match the experimental 
ones. Moreover, the simulation has to match the data acquisition (DAQ) features 
that can lead to cutting out hits. After setting the simulation properly, we 
compared simulation to experiment on an event by event basis as shown in 
figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
as the ratio of the measured ADCs to the simulated deposited energy.  
{\color{blue} Then, the gain of each readout pad is corrected by a factor, that 
is defined as the ratio of the ADC value of each pad to the ADCs of the other 
pads inside each track to make sure that the recorded ADCs by a given pad are 
similar to the recorded ADCs recorded by other pads in the same track.}

{\bf \color{red} Mohammad: Detail are missing here.}
Results of this second method are shown in Figure~\ref{fig:dedx_p_exp_2nd},
from these we concluded that the gains of the 
second method match best the theoretical lines.
